
\documentclass[12pt]{book}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage{algorithm}
\usepackage{algpseudocode}

\usepackage{fancyheadings}
\usepackage{setspace}
\usepackage{color}
\usepackage{caption}
\usepackage{float}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{float}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lipsum}
\usepackage{imakeidx}
\usepackage[bookmarksnumbered=true,colorlinks=true,linkcolor=blue]{hyperref}

\textwidth=17cm
\textheight=22.5cm

\setlength{\oddsidemargin}{-0.1in}
\setlength{\evensidemargin}{-0.1in}

\topmargin=3pt
\abovecaptionskip=3pt
\belowcaptionskip=3pt


\marginparwidth 0pt \marginparsep 10pt
\columnsep 0.5in \parindent  18pt   \parskip  0pt
\setlength{\itemsep}{.5pt}
\setlength{\parsep}{0pt}
\setlength\parindent{0pt}
\setcounter{secnumdepth}{4}

\definecolor{verbgray}{gray}{0.9}

\lstnewenvironment{evb}{%
      \lstset{backgroundcolor=\color{verbgray},
        frame=single, framerule=0pt, basicstyle=\footnotesize\ttfamily,
              columns=fullflexible, keepspaces=true, belowskip=0.3cm}}{}

\definecolor{shadecolor}{rgb}{.9, .9, .9}

%%%%%% nverb
\lstset{
        basicstyle=\color{blue} \ttfamily,
}
\lstdefinestyle{inline}{
    columns=fullflexible,breaklines=true
}
\newcommand{\nverb}[1]{\lstinline[style=inline]!#1!}

\pagestyle{fancy}

\fancyhead[RE]{\leftmark}
\fancyhead[LO]{\rightmark}
\fancyhead[LE,RO]{}
\renewcommand\sectionmark[1]{\markright{\thesection.\ #1}}

\newcommand{\namelistlabel}[1]{\mbox{#1}\hfill}
\newenvironment{namelist}[1]{%
\begin{list}{}
  {\let\makelabel\namelistlabel
  \settowidth{\labelwidth}{#1}
  \setlength{\leftmargin}{1.1\labelwidth}}
  }{%
\end{list}}

\makeindex

\begin{document}

\begin{titlepage}
\begin{center}

\vspace{5cm}
\begin{spacing}{2.5}
\vspace{5cm}
\textbf{} \\[1.5cm]
\textbf{\Huge SXAMG: a Serial Algebraic Multigrid Solver Library} \\[0.5cm]
\textbf{VERSION 1.0}
\vspace*{\fill}
\end{spacing}

\begin{spacing}{1.15}
\textnormal{\large Hui Liu}
\end{spacing}
\end{center}
\end{titlepage}

\tableofcontents

\setlength{\parskip}{8pt}

\clearpage
\pagenumbering{arabic}

\include{intro}
\include{install}
\include{basics}
\include{solver}
\include{utils}
\include{demo}

\begin{thebibliography}{00}

\bibitem{FASP}
    Xiaozhe Hu, Wei Liu, Guan Qin, Jinchao Xu, Zhensong Zhang,Development of A Fast Auxiliary Subspace
    Pre-conditioner for Numerical Reservoir Simulators, SPE-148388-MS, SPE Reservoir Characterisation and
    Simulation Conference and Exhibition, 9-11 October, Abu Dhabi, UAE.

\bibitem{Stuben2}
    {JW Ruge and K St\"{u}ben}, {Algebraic multigrid (AMG)},
    in: S.F. McCormick (Ed.), Multigrid Methods, Frontiers in Applied Mathematics, Vol. 5, SIAM, Philadelphia, 1986.

\bibitem{BMR}
    {A Brandt, SF McCormick, J Ruge},
    Algebraic multigrid (AMG) for sparse matrix equations
    D.J. Evans (Ed.), Sparsity and its Applications, Cambridge University Press, Cambridge, 1984, 257--284.

\bibitem{falgout}
    RD Falgout, An Introduction to Algebraic Multigrid, Computing in Science and Engineering,
    Special Issue on Multigrid Computing, 8, 2006, 24--33.

\bibitem{AMG-OR}
    K. St\"{u}ben, T. Clees, H. Klie, B. Lou, M.F. Wheeler,
    Algebraic multigrid methods (AMG) for the efficient solution of fully implicit formulations in reservoir simulation,
    SPE Reservoir Simulation Symposium. 2007.

\bibitem{AMG}
    K. St\"{u}ben,
    A review of algebraic multigrid,
    Journal of Computational and Applied Mathematics 128.1 (2001): 281-309.

\bibitem{psm}
    UM Yang, On the Use of Relaxation Parameters in Hybrid Smoothers,
    Numerical Linear Algebra With Applications, 11, (2004), 155-172.

\bibitem{rsamg}
    {AJ Cleary, RD Falgout, VE Henson, JE Jones, TA Manteuffel, SF McCormick,
    GN Miranda, JW Ruge}, {Robustness and Scalability of Algebraic Multigrid}, SIAM J. Sci. Comput., 21, 2000, 1886--1908.

\bibitem{HYPRE2}
    R. D. Falgout, and U.M. Yang, HYPRE: A library of high performance preconditioners,
    Lecture Notes in Computer Science, Springer Berlin Heidelberg, 2002. 632-641.

\bibitem{cljp1}
    AJ Cleary, RD Falgout, VE Henson, JE Jones, Coarse grid selection for parallel algebraic multigrid, in Proceedings of the
    fifth international symposium on solving irregularly structured problems in parallel, Springer-Verlag, New York, 1998.

\bibitem{cljp2}
    MT Jones, PE Plassman, A parallel graph coloring heuristic, SIAM Journal on Scientific Computing, 14(1993): 654-669.

\bibitem{cljp3}
    M Luby, A simple parallel algorithm for the maximal independent set problem,
    SIAM Journal on Computing, 15(1986), 1036-1053.

\bibitem{pmis}
    Hans~DS, Yang~UM, Heys~J,
    Reducing Complexity in Parallel Algebraic Multigrid Preconditioners,
    SIAM Journal on Matrix Analysis and Applications 27, (2006), 1019-1039.

\end{thebibliography}

\end{document}
